\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-30 papers/jfp/5-rebuilders.tex
Fix two typos, drop repeated text

The \Shake build system and the associated paper -- see~\S2.3.3
in~Mitchell~\shortcite{mitchell2012shake} -- use a slightly different trace
structure, called \emph{verifying step traces},
which stores less data than veryifying traces, and has slightly different early cutoff semantics. Rather than
storing the \hs{Hash}~\hs{v} for each dependency, it instead stores \hs{built}
time and \hs{changed} time for each \hs{key}, and a list of dependency keys
(without the hashes). The resulting \hs{StepTrace} type resembles:

@@

Current build systems using deep constructive traces always record hashes of
terminal \emph{input keys}, but the technique works equally well if we skip any
number of dependency levels (say $n$ levels). The input-only approach is the
special case of $n = \infty$, and constructive traces are the special case of
$n = 1$. By picking values of $n$ in between we would regain some early cutoff, at the
cost of losing such simple shallow builds and still requiring determinstic tasks.

>>>>

The \Shake build system and the associated paper -- see~\S2.3.3
in~Mitchell~\shortcite{mitchell2012shake} -- use a slightly different trace
structure, called \emph{verifying step traces},
which stores less data than verifying traces, and has slightly different early cutoff semantics. Rather than
storing the \hs{Hash}~\hs{v} for each dependency, it instead stores \hs{built}
time and \hs{changed} time for each \hs{key}, and a list of dependency keys
(without the hashes). The resulting \hs{StepTrace} type resembles:

@@

Current build systems using deep constructive traces always record hashes of
terminal \emph{input keys}, but the technique works equally well if we skip any
number of dependency levels (say $n$ levels). The input-only approach is the
special case of $n = \infty$, and constructive traces are the special case of
$n = 1$. By picking values of $n$ in between we would regain some early cutoff, at the
cost of losing such simple shallow builds and still requiring deterministic tasks.
